Multisensor Architecture for an Intersection Management System

### 2019-01-28 ch4-results.tex
Figure merged in section 3.3 and added results summary as table 3.3

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level. In this case, the binary status of a leg (traffic flowing, traffic stopped) is the metric used for evaluation, derived from the vehicle count.

The table \ref{desc_test_config} lists all used blocks and assigns an ID for each one. Those IDs are used in the graph description in its own section. Also, bold nodes and connections indicate multiple instance of the same element. The figure \ref{tconf2} shows the  configuration used for processing just video data the configuration when a set of lasers is added to the previous configuration. The blue line represents the fusion at node K, which is fusion on virtual sensors level. The purple line represents the fusion at flow rate level.

\todo{Explain evaluation params}

@@

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.45]{fig/4/video_res.pdf}
\caption{Results for the single camera implementation in one of the legs of the intersection}
\label{video_res}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/laser1a.png}
\caption{Vehicle detection using laser scanners}
\label{laser_detection}
\end{figure}

@@

When the fusion is performed at flow rate level using average policy, the accuracy and TPR values are reduced to 84.45\% and 12.92\%. Using maximum policy, there is a small decrement in the values, with an accuracy of 89.76\% and a TPR of 57.46\%.

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-rigth, Maximum on flow rate}
\label{vl_cf}
\end{figure}

@@

@@

\todo{Sumarise and discuss results}

\begin{table}[ht!]
\footnotesize
\begin{tabular}{c c c c c}
Test Case & Sensors & Fusion Aproaches & Accuracy & TPR \\

Case 1 & Camera & NA & 91.82\% & 55.7\% \\
Case 2 & Camera + Lasers & Low-level, Mid-level (avg) & 92.2\% & 88.12\%\\
Case 2 & Camera + Lasers & Low-level, Mid-level (max) & 91.48\% & 63.56\% \\
Case 2 & Camera + Lasers & Low-level, High-level (avg) & 84.45\% & 12.92\% \\
Case 2 & Camera + Lasers & Low-level, High-level (max) & 89.76\% & 57.46\%\\

\end{tabular}
\caption{Summary of results}
\label{results}
\end{table}

@@

For different sources of information it is not enough to perform a fusion strategy to obtain better results. It is needed to analyse the type of data and the level at which fusion should be performed. Also, it is important to understand if the fusion is competitive, complementary or cooperative, in order to select the appropiate strategy and increase the performance of the system. An example of this, was found when fusing data from camera and lasers at two different levels and using different strategies. It was clear from the results that altough the data was the same, one configuration increased the performace while another one decrease it.

>>>>

Each configuration consists of a set of processing blocks (as described in section \ref{proc_blocks}) connected, aiming to take data from  lasers and cameras, to produce an output of higher level. In this case, the binary status of a leg (traffic flowing, traffic stopped) is the output used for evaluation, derived from the vehicle count.

The table \ref{desc_test_config} lists all used blocks and assigns an ID for each one. Those IDs are used in the graph description in its own section. Also, bold nodes and connections indicate multiple instance of the same element. The figure \ref{tconf2} shows the  configuration used for processing just video data the configuration when a set of lasers is added to the previous configuration. The blue line represents the fusion at node K, which is fusion on virtual sensors level (Mid-level fusion). The purple line represents the fusion at flow rate level (High-level fusion).

@@

As this is a binary classification system, the evaluation metrics used for these implementations, derived from the obtained confusion matrices, are Accuracy and True Positive Rate (TPR).
%TODO

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.42]{fig/4/video_res.pdf}
\caption{Results for the single camera implementation in one of the legs of the intersection}
\label{video_res}
\end{figure}

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.35]{fig/4/laser1a.png}
\caption{Vehicle detection using laser scanners}
\label{laser_detection}
\end{figure}

@@

When the fusion is performed at flow rate level using average policy, the accuracy and TPR values are reduced to 84.45\% and 12.92\%. Using maximum policy, there is a small decrement in the values, with an accuracy of 89.76\% and a TPR of 57.46\%. A summary of the results obtained on both test cases is presented in table \ref{results}.

% It can be seen in this table that merging laser data with video data in some cases enhance the classification task. But it should be noted that this is an unbalanced dataset, with 17.64 \% of True (Flowing traffic) instances and 82.36 \% of False (Stopped traffic),

@@

\begin{figure}[htb!]
\centering
\includegraphics[scale=0.4]{fig/4/conf_mat.jpeg}
\caption{Fusion configurations: top-left, Average on virtual sensor occupancy. Bottom-left, Maximum on virtual sensor occupancy. Top-right, Average on flow rate. Bottom-right, Maximum on flow rate}
\label{vl_cf}
\end{figure}

@@

%\subsection{Discussion}

%\todo{Sumarise and discuss results}

\begin{table}[ht!]
\footnotesize
\begin{tabular}{|c| c| c| c| c|}

\hline
\textbf{Test Case} & \textbf{Sensors} & \textbf{Fusion Aproaches} & \textbf{Accuracy} & \textbf{TPR} \\
\hline
Case 1 & Camera & NA & 91.82\% & 55.7\% \\
\hline
Case 2 & Camera + Lasers & Low-level, Mid-level (avg) & 92.2\% & 88.12\%\\
\hline
Case 2 & Camera + Lasers & Low-level, Mid-level (max) & 91.48\% & 63.56\% \\
\hline
Case 2 & Camera + Lasers & Low-level, High-level (avg) & 84.45\% & 12.92\% \\
\hline
Case 2 & Camera + Lasers & Low-level, High-level (max) & 89.76\% & 57.46\%\\
\hline
\end{tabular}
\caption{Summary of results}
\label{results}
\end{table}

@@

@@

For different sources of information it is not enough to perform a fusion strategy to obtain better results. It is needed to analyse the type of data and the level at which fusion should be performed. Also, it is important to understand if the fusion is competitive, complementary or cooperative, in order to select the appropiate strategy and increase the performance of the system. An example of this was demonstrated when fusing data from camera and lasers at two different levels and using different strategies. It was clear from the results (table \ref{results}) that altough the data was the same, one configuration increased the performace while another one decrease it.
